---
title: "Lab11"
author: "Luis Mario Trevisi"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1

```{r}
getwd()
```

# Task 2

## Using R as calculator

```{r}
d=c(5.0581, 4.9707, 5.0893, 4.9334, 4.9777, 5.0285, 4.8555, 4.9565, 
4.9769, 4.9722, 4.999, 4.9925, 4.9686, 5.0662, 4.9239, 4.9781, 
5.0485, 5.0014, 4.9957, 5.0195, 5.0118, 4.9928, 5.0361, 5.0185, 
4.9879)

# For 95% Confidence
# Lower Interval 

mean(d)-qt(1-0.05/2,length(d))*(sd(d)/sqrt(length(d)))



# Upper Interval 

mean(d)+qt(1-0.05/2,length(d))*(sd(d)/sqrt(length(d)))

# For 90% Confidence
# Lower Interval 

mean(d)-qt(1-0.1/2,length(d))*(sd(d)/sqrt(length(d)))



# Upper Interval 

mean(d)+qt(1-0.1/2,length(d))*(sd(d)/sqrt(length(d)))

# For 80% Confidence
# Lower Interval 

mean(d)-qt(1-0.2/2,length(d))*(sd(d)/sqrt(length(d)))



# Upper Interval 

mean(d)+qt(1-0.2/2,length(d))*(sd(d)/sqrt(length(d)))

# For 50% Confidence
# Lower Interval 

mean(d)-qt(1-0.5/2,length(d))*(sd(d)/sqrt(length(d)))



# Upper Interval 

mean(d)+qt(1-0.5/2,length(d))*(sd(d)/sqrt(length(d)))

```

## Using t.test

```{r}
d=c(5.0581, 4.9707, 5.0893, 4.9334, 4.9777, 5.0285, 4.8555, 4.9565, 
4.9769, 4.9722, 4.999, 4.9925, 4.9686, 5.0662, 4.9239, 4.9781, 
5.0485, 5.0014, 4.9957, 5.0195, 5.0118, 4.9928, 5.0361, 5.0185, 
4.9879)

t.test(d,conf.level=0.8)$conf.int
```

## Using R as calculator 

```{r}
d=c(5.0581, 4.9707, 5.0893, 4.9334, 4.9777, 5.0285, 4.8555, 4.9565, 
4.9769, 4.9722, 4.999, 4.9925, 4.9686, 5.0662, 4.9239, 4.9781, 
5.0485, 5.0014, 4.9957, 5.0195, 5.0118, 4.9928, 5.0361, 5.0185, 
4.9879)

#For 95% Confidence
# Lower Interval 

(length(d)-1)*var(d)/qchisq(1-0.05/2,length(d)-1)

# Upper Interval 

(length(d)-1)*var(d)/qchisq(0.05/2,length(d)-1)

#For 90% Confidence
# Lower Interval 

(length(d)-1)*var(d)/qchisq(1-0.1/2,length(d)-1)

# Upper Interval 

(length(d)-1)*var(d)/qchisq(0.1/2,length(d)-1)

#For 80% Confidence
# Lower Interval 

(length(d)-1)*var(d)/qchisq(1-0.2/2,length(d)-1)

# Upper Interval 

(length(d)-1)*var(d)/qchisq(0.2/2,length(d)-1)

#For 50% Confidence
# Lower Interval 

(length(d)-1)*var(d)/qchisq(1-0.5/2,length(d)-1)

# Upper Interval 

(length(d)-1)*var(d)/qchisq(0.5/2,length(d)-1)

```

# Task 3

## ublue-usnapper r as calculator

```{r}
blue=c(21.65, 17.48, 20.1, 21.57, 14.82, 19.17, 21.08, 18.23, 22.93, 15.66, 20.89, 21.66, 18.5, 20.59, 18.63, 18.91, 19.53, 17.7, 16.5, 19.03)
snapper=c(31.65, 27.48, 30.1, 31.57, 24.82, 29.17, 31.08, 28.23, 32.93, 25.66, 30.89, 31.66, 28.5, 30.59, 28.63)

Spsqr = ((length(blue)-1)*var(blue)+(length(snapper)-1)*var(snapper))/(length(blue)+length(snapper)-2)
talpha2 = qt(1-0.05/2,length(blue)+length(snapper)-2)
#Upper Bound
mean(blue)-mean(snapper)+talpha2*sqrt(Spsqr*((1/length(blue))+(1/length(snapper))))
#Lower Bound
mean(blue)-mean(snapper)-talpha2*sqrt(Spsqr*((1/length(blue))+(1/length(snapper))))
 
```

## usnapper-ublue r as calculator

```{r}
blue=c(21.65, 17.48, 20.1, 21.57, 14.82, 19.17, 21.08, 18.23, 22.93, 15.66, 20.89, 21.66, 18.5, 20.59, 18.63, 18.91, 19.53, 17.7, 16.5, 19.03)
snapper=c(31.65, 27.48, 30.1, 31.57, 24.82, 29.17, 31.08, 28.23, 32.93, 25.66, 30.89, 31.66, 28.5, 30.59, 28.63)

Spsqr = ((length(blue)-1)*var(blue)+(length(snapper)-1)*var(snapper))/(length(blue)+length(snapper)-2)
talpha2 = qt(1-0.05/2,length(blue)+length(snapper)-2)
# Upper Bound
mean(snapper)-mean(blue)+talpha2*sqrt(Spsqr*((1/length(blue))+(1/length(snapper))))
# Lower Bound
mean(snapper)-mean(blue)-talpha2*sqrt(Spsqr*((1/length(blue))+(1/length(snapper))))
 
```

##	Give a practical interpretation of the above interval.

this means that 95% of the time the difference in mean between the samples of snappers and blue cod would lay on the interval previously calculated (8.75,11.84) and 95% of the times the difference in mean between the samples of blue cod and snapper would lay in the interval previously calculated (-11.84,-8.75). this also implies that the mean of the sample for snapper is bigger that the mean of the blue cod in 95% of the cases.

## Using t.test 

```{r}
blue=c(21.65, 17.48, 20.1, 21.57, 14.82, 19.17, 21.08, 18.23, 22.93, 15.66, 20.89, 21.66, 18.5, 20.59, 18.63, 18.91, 19.53, 17.7, 16.5, 19.03)
snapper=c(31.65, 27.48, 30.1, 31.57, 24.82, 29.17, 31.08, 28.23, 32.93, 25.66, 30.89, 31.66, 28.5, 30.59, 28.63)
t.test(snapper,blue,var.equal=TRUE,conf.level=0.95)$conf.int
t.test(snapper,blue,var.equal=TRUE,conf.level=0.85)$conf.int
t.test(snapper,blue,var.equal=TRUE,conf.level=0.75)$conf.int
t.test(snapper,blue,var.equal=TRUE,conf.level=0.25)$conf.int
```

##	What happens to the interval as the confidence level decreases?

as the confidence level decreases the interval becomes narrower/shorter.

# Task 4

## R calculater with 95% confidence

```{r}
Exam1=c(40.98, 59.36, 46.69, 41.8, 61.63, 65.31, 62.96, 60.21, 56.89, 
78.41, 53.44, 75.2, 60.54, 52.43, 41.41, 70.79, 73.55, 55.65, 
61.43, 63.84, 58.07, 53.79, 54.45, 67.18, 44.46)

Exam2=c(50.22, 66.19, 58.75, 51.88, 66.61, 70.86, 74.25, 70.23, 69.55, 
87.18, 63.62, 81.7, 70.5, 66.02, 51.35, 80.92, 85.65, 65.44, 
74.37, 75.28, 67.86, 59.92, 64.42, 73.57, 57.15)
length(Exam1)
length(Exam2)
d = Exam1-Exam2
# Upper bound
mean(d)+ qt(1-0.05/2,length(Exam1)-1) * sd(d)/sqrt(length(Exam1))
#Lower bound
mean(d)- qt(1-0.05/2,length(Exam1)-1) * sd(d)/sqrt(length(Exam1))

```

##	Interpret the interval practically

On average the students did better on exam 2 than on exam 1. this improvements has a 95% confidence of happening.


## Using T.test


```{r}
Exam1=c(40.98, 59.36, 46.69, 41.8, 61.63, 65.31, 62.96, 60.21, 56.89, 
78.41, 53.44, 75.2, 60.54, 52.43, 41.41, 70.79, 73.55, 55.65, 
61.43, 63.84, 58.07, 53.79, 54.45, 67.18, 44.46)

Exam2=c(50.22, 66.19, 58.75, 51.88, 66.61, 70.86, 74.25, 70.23, 69.55, 
87.18, 63.62, 81.7, 70.5, 66.02, 51.35, 80.92, 85.65, 65.44, 
74.37, 75.28, 67.86, 59.92, 64.42, 73.57, 57.15)

# Checking for equal variance
var.test(Exam1,Exam2,conf.level=0.95)
# 90% confidence
t.test(Exam1,Exam2,var.equal=TRUE,paired = TRUE, conf.level=0.9)$conf.int
# 80% confidence
t.test(Exam1,Exam2,var.equal=TRUE,paired = TRUE, conf.level=0.8)$conf.int
# 70% confidence
t.test(Exam1,Exam2,var.equal=TRUE,paired = TRUE, conf.level=0.7)$conf.int
# 60% confidence
t.test(Exam1,Exam2,var.equal=TRUE,paired = TRUE, conf.level=0.6)$conf.int
# 10% confidence
t.test(Exam1,Exam2,var.equal=TRUE,paired = TRUE, conf.level=0.1)$conf.int

```

# Task 5

## Making the table from data 

```{r}
B = read.csv('NZBIRDS.csv')

A = with(B,table(B$Extinct,B$Flight))

A = addmargins(A, margin = seq_along(dim(A)), FUN = sum, quiet = FALSE)

colnames(A) <- c("Number of flightless species","Number of flight species","Number of species sampled")
rownames(A) <- c("Non extinct","Extinct","")
A<-A[-c(3),] 
A<-A[,-c(2)]
A
```

## Using R as Calculator

```{r}
p1 = 21/(21+7)
q1 = 1-p1
p2=7/(21+7)
q2=1-p2
n1=21
n2=7
# Lower bound 
(p1-p2)-qnorm(1-0.05/2)*sqrt((p1*q1/n1)+(p2*q2/n2))
# Upper bound
(p1-p2)+qnorm(1-0.05/2)*sqrt((p1*q1/n1)+(p2*q2/n2))

```

# Task 6

## Using R as calculator

```{r}
	set.seed(35);sam1=rnorm(25,mean=10,sd=5);
  set.seed(45);sam2=rnorm(34,mean=40,sd=8)
# Lower bound
(var(sam1)/var(sam2))*(1/(qf(1-0.05/2,length(sam1)-1,length(sam2)-1)))
# Upper bound
(var(sam1)/var(sam2))*qf(1-0.05/2,length(sam2)-1,length(sam1)-1)

```
## Using Var.test

```{r}
set.seed(35);sam1=rnorm(25,mean=10,sd=5);
  set.seed(45);sam2=rnorm(34,mean=40,sd=8)

var.test(sam1,sam2,conf.level=0.8)$conf.int
var.test(sam1,sam2,conf.level=0.7)$conf.int
var.test(sam1,sam2,conf.level=0.6)$conf.int
var.test(sam1,sam2,conf.level=0.5)$conf.int
```

# Task 7

```{r}
set.seed(23);x = rnorm(30,mean=10,sd=12)
MATH4753ouTrev0002::myci(x,conf.int=0.95)

```

