---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753ouTrev0002)
```

# Functions

## myhyper

creates a simulation of a hypergeometric probability using the number of iterations, the total number of elemetents, the number of success in the N elements and the number of elements drawn

## myci

creates the confidence interval of the mean given the samples and the confindence on the interval 

## mychisim

creates a simulation for 1 parameter chi-square statistic using the sample size, standard deviation of the population, mean of the population and number of iterations

## mychisim2 

creates a simulation for 2 parameter chi-square statistic using the sample size, standard deviation of the population, mean of the population and number of iterations of both sample populations
