---
title: "Lab1"
author: "Luis Mario Trevisi"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Tasks

## Task 1

Find the working directory

```{r}
getwd()
```

## Task 2

Read in the DDT data

```{r}
ddt <- read.csv("DDT.csv")
head(ddt)
```


## Task 3

  a. Qualitative Variables: River, Species
  b. Quantitative Variables: Mile, Length, Weight, DDT

Q.1 Find the mean length of fish in the ddt data frame!

$Mean = \frac{\sum_{i=1}^n y_i}{n}$ where n is the number of data points

```{r}
meanvalue = c(mean(ddt$LENGTH))
meanvalue
```
Q.2 What is the standard deviation of the weight of fish in the ddt data frame?

$$s = \sqrt{\frac{\sum^n_{i=1} (y_i-\bar{y})^2}{n-1}} $$

```{r}
sd(ddt$WEIGHT)
```

Q3. Is this the plot of LENGTH vs WEIGHT from the ddt data frame?

```{r}
plot(ddt$WEIGHT,ddt$LENGTH)
```

No (0)

Q4. If v=1:20 what is the last value of v/20?

```{r}
v=1:20
v/20
```
ans: 1

## Task 4

Table of the Rivers

```{r}
table(ddt$RIVER)
```

Barplot of the Rivers

```{r}
table(ddt$RIVER)->tab
barplot(tab,col = 1:4, main="Rivers")

```

Table of the rivers crossed with the species of fish

```{r}
spriv=with(ddt,table(SPECIES,RIVER))
spriv
```

barplot of the rivers crossed with the species of fish

```{r}
spriv=with(ddt,table(ddt$SPECIES,ddt$RIVER))
barplot(height = spriv,col=1:3,beside=TRUE,axes=TRUE)
legend("topleft",legend =(c("CCATFISH","LMBASS","SMBUFFALO")),fill = c(col=1:3), bty ="n", bg ="transparent")

```

## Task 5

Pie chart of Fish Species

```{r}
pie(table(ddt$SPECIES))
```

Pie chart of Rivers

```{r}
pie(table(ddt$RIVER))
```

## Task 6 

Boxplot of the variable DDT

```{r}
with(ddt,boxplot(DDT,ylab="DDT",col="Blue",notch=TRUE))
```
Boxplot of the variable WEIGHT

```{r}
with(ddt,boxplot(WEIGHT,ylab="WEIGHT",col="Blue",notch=TRUE))
```

Boxplot of the variable LENGTH

```{r}
with(ddt,boxplot(LENGTH,ylab="LENGTH",col="Blue",notch=TRUE))
```


## Task 7

Coplot of LENGTH Vs WEIGHT given RIVER

```{r}
coplot(LENGTH~WEIGHT|RIVER,data=ddt,col=1:4)
```

Coplot of DDT Vs WEIGHT given SPECIES

```{r}
coplot(DDT~WEIGHT|SPECIES,data=ddt,col=1:3)
```


## Task 8

Plot 1

```{r}

```

