---
title: "Lab1"
author: "Luis Mario Trevisi"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Tasks

## Task 1

Find the working directory

```{r}
getwd()
```

## Task 2

Read in the DDT data

```{r}
ddt <- read.csv("DDT.csv")
head(ddt)
```


## Task 3

  a. Qualitative Variables: River, Species
  b. Quantitative Variables: Mile, Length, Weight, DDT
  c. Three Species
  d. see below 
  
```{r}
p = with(ddt, ddt[WEIGHT>800 & SPECIES=="LMBASS",])
p
```

  e.see below
  
```{r}
p = with(ddt, ddt[DDT>4.0 & RIVER=="SCM",])
p
```
## IClicker

Q.1 Find the mean length of fish in the ddt data frame!

$Mean = \frac{\sum_{i=1}^n y_i}{n}$ where n is the number of data points

```{r}
meanvalue = c(mean(ddt$LENGTH))
meanvalue
```
Q.2 What is the standard deviation of the weight of fish in the ddt data frame?

$$s = \sqrt{\frac{\sum^n_{i=1} (y_i-\bar{y})^2}{n-1}} $$

```{r}
sd(ddt$WEIGHT)
```

Q3. Is this the plot of LENGTH vs WEIGHT from the ddt data frame?

```{r}
with(ddt,plot(WEIGHT,LENGTH))
```

No (0)

Q4. If v=1:20 what is the last value of v/20?

```{r}
v=1:20
v/20
```
ans: 1

## Task 4

Table of the Rivers

```{r}
table(ddt$RIVER)
```

Barplot of the Rivers

```{r}
table(ddt$RIVER)->tab
barplot(tab,col = 1:4, main="Rivers")

```

Table of the rivers crossed with the species of fish

```{r}
spriv=with(ddt,table(RIVER,SPECIES))
spriv
```

barplot of the rivers crossed with the species of fish

```{r}
spriv=with(ddt,table(ddt$RIVER,ddt$SPECIES))
barplot(height = spriv,col=1:3,beside=TRUE,axes=TRUE)
legend("topleft",legend =(c("CCATFISH","LMBASS","SMBUFFALO")),fill = c(col=1:3), bty ="n", bg ="transparent")

```

## Task 5

Pie chart of Fish Species

```{r}
pie(table(ddt$SPECIES))
```

Pie chart of Rivers

```{r}
pie(table(ddt$RIVER))
```

## Task 6 

Boxplot of the variable DDT

```{r}
with(ddt,boxplot(DDT,ylab="DDT",col="Blue",notch=TRUE))
```

Boxplot of the variable WEIGHT

```{r}
with(ddt,boxplot(WEIGHT,ylab="WEIGHT",col="Blue",notch=TRUE))
```

Boxplot of the variable LENGTH

```{r}
with(ddt,boxplot(LENGTH,ylab="LENGTH",col="Blue",notch=TRUE))
```


## Task 7

Coplot of LENGTH Vs WEIGHT given RIVER

```{r}
rivcol=with(ddt, ifelse(RIVER=="FCM","Red",
                        ifelse(RIVER=="LCM","Blue",
                               ifelse(RIVER=="SCM","Green","Black"))))
coplot(LENGTH~WEIGHT|RIVER,data=ddt,col=rivcol)

```

Coplot of DDT Vs WEIGHT given SPECIES

```{r}
fishcol=with(ddt,ifelse(SPECIES=="CCATFISH","Red",
                        ifelse(SPECIES=="SMBUFFALO","Blue","Green")))
coplot(DDT~WEIGHT|SPECIES,data=ddt,col=fishcol)
```


## Task 8

Plot 1

```{r}
library(ggplot2)
g = ggplot(ddt, aes(x=SPECIES, y= WEIGHT, fill = RIVER) )
g = g + geom_boxplot()+ggtitle("Luis Mario Trevisi")
g
```

Plot 2

```{r}
library(ggplot2)
g = ggplot(ddt, aes(x=RIVER, y= LENGTH, fill = SPECIES) )
g = g + geom_violin() +ggtitle("Luis Mario Trevisi")
g
```

Plot 3

```{r}
library(ggplot2)
g = ggplot(ddt, aes(x=WEIGHT, y= LENGTH, color = SPECIES) )
g = g + geom_point() +ggtitle("Luis Mario Trevisi")
g
```

