---
title: "Lab10"
author: "Luis Mario Trevisi"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1

```{r}
getwd()
```

# Task 2

```{r}
mymaxlik=function(lfun,x,param,...){
# how many param values are there?
np=length(param)
# outer -- notice the order, x then param
# this produces a matrix – try outer(1:4,5:10,function(x,y) paste(x,y,sep=" "))   to understand
z=outer(x,param,lfun) # A
# z is a matrix where each x,param is replaced with the function evaluated at those values
y=apply(z,2,sum)

# y is a vector made up of the column sums
# Each y is the log lik for a new parameter value
plot(param,y,col="Blue",type="l",lwd=2,...)
# which gives the index for the value of y >= max.
# there could be a max between two values of the parameter, therefore 2 indices
# the first max will take the larger indice
i=max(which(y==max(y))) # B
abline(v=param[i],lwd=2,col="Red")

# plots a nice point where the max lik is
points(param[i],y[i],pch=19,cex=1.5,col="Black")
axis(3,param[i],round(param[i],2))
#check slopes. If it is a max the slope should change sign from + to 
# We should get three + and two -vs
ifelse(i-3>=1 & i+2<=np, slope<-(y[(i-2):(i+2)]-y[(i-3):(i+1)])/(param[(i-2):(i+2)]-param[(i-3):(i+1)]),slope<-"NA")
return(list(i=i,parami=param[i],yi=y[i],slope=slope))
}

```

## Line code explanantion 

Line A: it creates a matrix with the results of applying a function to array x and y. in this sense it would produce a matrix with size(y) rows and size(x) columns. thus in the case of this line it would apply the function lfun between matrix x and param, producing all possible combinations as a outcome matrix which would have a size of size(x) columns and size(param) rows.

Line B: in this line we are finding the biggest indices where the logical test y == max(y) is true and storing it on the variable i. breaking down this procedure, the which function would give all the indices where the logical test y=max(y) is true, and then the outer max function would find the biggest index from the ouput of the output of the which function.

## What is the formula (mathematical – no R code) for the likelihood?

$p(y_1,y_2,y_3,y_4,y_5,y_6,y_7,y_8) = p(y_1)p(y_2)p(y_3)p(y_4)p(y_5)p(y_6)p(y_7)p(y_8)$ $$= {20 \choose y_1} p^{y_1}(1-p)^{20-y_1}  {20 \choose y_2} p^{y_2}(1-p)^{20-y_2} \cdots  {20 \choose y_8} p^{y_8}(1-p)^{20-y_8} = \prod_{i=1}^{8} {20 \choose y_i}p^{y_i}(1-p)^{20-y_i}$$

##	What is the R code for the above likelihood?
```{r}
#dbinom(y1,20,p)*dbinom(y2,20,p)*dbinom(y3,20,p)*dbinom(y4,20,p)*dbinom(y5,20,p)*dbinom(y6,20,p)*dbinom(y7,20,p)*dbinom(y8,20,p)
```

## 	Find the maximum likelihood estimate when the following is the data y=3,3,4,3,4,5,5,4 (record the plot).

```{r}
y=c(3,3,4,3,4,5,5,4)
logbin = function(x,param){log(dbinom(x,prob=param,size=20))}
mymaxlik(lfun=logbin, x=y, param = seq(0,1,length = 1000), main = "binomial, n=20")
```

# Task 3

## Max Likelihood


```{r}
y = c(4,6,7,6,5)
logpoiss = function(x,param){log(dpois(x,lambda=param))}
mymaxlik(x=y,param=seq(0,10,length=1000),lfun=logpoiss,xlab=expression(lambda),main="Poisson",cex.main=1)
```

thus, $\lambda = 5.6$


$p(y_1,y_2,y_3,y_4,y_5,y_6,y_7,y_8) = p(y_1)p(y_2)p(y_3)p(y_4)p(y_5)p(y_6)p(y_7)p(y_8)$

$$L(\lambda) = \prod_{i=1}^5 \frac{e^{-5\lambda}\lambda^{\sum y_i}}{y_i!}$$

$$ l(\lambda) = log(e^{-5\lambda})+\prod_{i=1}^{5}log(\lambda^{\sum y_i})-\prod_{i=1}^{5}log(y_i!)$$

$$ t(\lambda) = -5\lambda+\prod_{i=1}^{5}y_i log(\lambda)-\prod_{i=1}^{5}log(y_i!) $$

## Using myNRML

```{r}
myNRML=function(x0,delta=0.001,llik,xrange,parameter="param"){
f=function(x) (llik(x+delta)-llik(x))/delta
fdash=function(x) (f(x+delta)-f(x))/delta
d=1000
i=0
x=c()
y=c()
x[1]=x0
y[1]=f(x[1])
while(d > delta & i<100){
i=i+1
x[i+1]=x[i]-f(x[i])/fdash(x[i])
y[i+1]=f(x[i+1])
d=abs(y[i+1])
}
layout(matrix(1:2,nr=1,nc=2,byrow=TRUE),width=c(1,2))
curve(llik(x), xlim=xrange,xlab=parameter,ylab="log Lik",main="Log Lik")
curve(f(x),xlim=xrange,xaxt="n", xlab=parameter,ylab="derivative",main=  "Newton-Raphson Algorithm \n on the derivative")
points(x,y,col="Red",pch=19,cex=1.5)
axis(1,x,round(x,2),las=2)
abline(h=0,col="Red")

segments(x[1:(i-1)],y[1:(i-1)],x[2:i],rep(0,i-1),col="Blue",lwd=2)
segments(x[2:i],rep(0,i-1),x[2:i],y[2:i],lwd=0.5,col="Green")

list(x=x,y=y)
}
myNRML(x0=1,delta=0.000001,llik=function(x) log(dpois(4,x)*dpois(6,x)*dpois(6,x)*dpois(7,x)*dpois(5,x)),xrange=c(0,30),parameter="lambda" )
```

thus, $\hat{\lambda} = 5.6$

# Task 4

```{r}
logbin2=function(theta){log(dbinom(2,prob=theta,size=6)) + log(dbinom(4,prob=theta,size=10))}

mymaxlikg=function(lfun="logbin2",theta) { # default log lik is a combination bin
nth=length(theta)  # nu. of valuse used in theta
thmat=matrix(theta,nr=nth,nc=1,byrow=TRUE) # Matrix of theta
z=apply(thmat,1,lfun) # z holds the log lik values
zmax=max(which(z==max(z)))  # finding the INDEX of the max lik
plot(theta,exp(z),type="l") # plot of lik
abline(v=theta[zmax],col="Blue")   #  verical line through max
axis(3,theta[zmax],round(theta[zmax],4))  # one tick on the third axis 
theta[zmax]   # theta corresponding to max lik
}
mymaxlikg(theta=seq(0,1,length=10000),lfun=logbin2)
```

# Task 5

## algebraic

$$L(\theta_1,\theta_2) = {n \choose y_1} \theta_1^{y_1}(1-\theta_1)^{n-y_1} \frac{e^{-\theta_2}\theta_2^{y_2}}{y_2!}$$

$$l(\theta_1,\theta_2) = log({n \choose y_1} \theta_1^{y_1}(1-\theta_1)^{n-y_1} \frac{e^{-\theta_2}\theta_2^{y_2}}{y_2!})$$

$$=log({n \choose y_1}) + y_1log(\theta_1)+(n-y_1)log(1-\theta_1)-\theta_2+y_2log(\theta_2)-log(y_2!)$$
$$= log(n!)-log(y_1!)-log((n-y_1)!)+y_1log(\theta_1)+(n-y_1)log(1-\theta_1)-\theta_2+y_2log(\theta_2)-log(y_2!)$$

## graphical maxima likelihood 
	Suppose the poisson process has $y_2=4$ and the binomial process n=20, $y_1=4$

```{r}
logbinpois=function(theta1,theta2) log(dbinom(4,size=20,prob=theta1)) +  log(dpois(4,lambda=theta2))

maxlikg2=function(theta1,theta2,lfun="logbinpois",...){
n1=length(theta1)
n2=length(theta2)
z=outer(theta1,theta2,lfun)
contour(theta1,theta2,exp(z),...) # exp(z) gives the lik
maxl=max(exp(z))    # max lik
coord=which(exp(z)==maxl,arr.ind=TRUE)  # find the co-ords of the max
th1est=theta1[coord[1]] # mxlik estimate of theta1
th2est=theta2[coord[2]]
abline(v=th1est,h=th2est)
axis(3,th1est,round(th1est,2))
axis(4,th2est,round(th2est,2),las=1)
list(th1est=th1est,th2est=th2est)
}
maxlikg2(theta1=seq(0,1,length=1000),theta2=seq(0,10,length=1000),nlevels=20)
```

# Task 6

Suppose that another experiment is performed this time data is generated from a beta distribution.

```{r}
mymlnorm=function(x,mu,sig,...){  #x sample vector
nmu=length(mu) # number of values in mu
nsig=length(sig)
n=length(x) # sample size
zz=c()    ## initialize a new vector
lfun=function(x,m,p) log(dnorm(x,mean=m,sd=p))   # log lik for normal
for(j in 1:nsig){
z=outer(x,mu,lfun,p=sig[j]) # z a matrix 
# col 1 of z contains lfun evaluated at each x with first value of mu, 
# col2 each x with 2nd value of m 
# all with sig=sig[j]
y=apply(z,2,sum)
# y is a vector filled with log lik values, 
# each with a difft mu and all with the same sig[j]
zz=cbind(zz,y)
## zz is the matrix with each column containing log L values, rows difft mu, cols difft sigmas 
}
maxl=max(exp(zz))
coord=which(exp(zz)==maxl,arr.ind=TRUE)
maxlsig=apply(zz,1,max)
contour(mu,sig,exp(zz),las=3,xlab=expression(mu),ylab=expression(sigma),axes=TRUE,
main=expression(paste("L(",mu,",",sigma,")",sep="")),...)
mlx=round(mean(x),2)  # theoretical
mly=round(sqrt((n-1)/n)*sd(x),2)
#axis(1,at=c(0:20,mlx),labels=sort(c(0:20,mlx)))
#axis(2,at=c(0:20,mly),labels=TRUE)
abline(v=mean(x),lwd=2,col="Green")
abline(h=sqrt((n-1)/n)*sd(x),lwd=2,col="Red")

# Now find the estimates from the co-ords
muest=mu[coord[1]]
sigest=sig[coord[2]]

abline(v=muest, h=sigest)
return(list(x=x,coord=coord,maxl=maxl))
}

mymlnorm(x=c(10,12,13,15,12,11,10 ),mu=seq(10,15,length=1000),sig=seq(0.1,4,length=1000),lwd=2,labcex=1)
```

# Task 7

```{r}
mymlbeta=function(x,alpha,beta,...){  #x sample vector
na=length(alpha) # number of values in alpha
nb=length(beta)
n=length(x) # sample size
zz=c()    ## initialize a new vector
lfun=function(x,a,b) log(dbeta(x,shape1=a,shape2=b))   # log lik for beta
for(j in 1:nb){
z=outer(x,alpha,lfun,b=beta[j]) # z a matrix 
# col 1 of z contains lfun evaluated at each x with first value of alpha, 
# col2 each x with 2nd value of a 
# all with b=beta[j]
y=apply(z,2,sum)
# y is a vector filled with log lik values, 
# each with a difft alpha and all with the same sig[j]
zz=cbind(zz,y)
## zz is the matrix with each column containing log L values, rows difft alpha, cols difft betas 
}
maxl=max(exp(zz))    # max lik
coord=which(exp(zz)==maxl,arr.ind=TRUE)  # find the co-ords of the max
aest=alpha[coord[1]] # mxlik estimate of alpha
best=beta[coord[2]]
contour(alpha,beta,exp(zz),las=3,xlab=expression(alpha),ylab=expression(beta),axes=TRUE,
main=expression(paste("L(",alpha,",",beta,")",sep="")),...)

abline(v=aest, h=best)
points(aest,best,pch=19)
axis(4,best,round(best,2),col="Red")
axis(3,aest,round(aest,2),col="Red")
return(list(x=x,coord=coord,maxl=maxl,maxalpha=aest,maxbeta=best))
}

## Examine the variability of the maximum likelihood from sample to sample
## This could form the core of a new function 
## Boot Max Lik
layout(matrix(1:12,nr=3,nc=4,byrow=TRUE))
z=c()
a=3
b=4
sam= rbeta(30,shape1=a,shape2=b)
nsam=length(sam)
for(i in 1:12){
w=mymlbeta(x=sample(sam,nsam,replace=TRUE),alpha=seq(0.1,20,length=100),beta=seq(0.1,20,length=100),lwd=2,labcex=1,col="steelblue")
points(a,b,col="Red",pch=19)
abline(v=a,h=b,col="Red")
z<-rbind(z,c(w$maxalpha,w$maxbeta))
 }
colnames(z)=c("alpha","beta")
z
dz=apply(z-c(a,b),1,function(x) sqrt(sum(x^2)) )
layout(matrix(1))
plot(dz)
which(dz>4)
```

# Task 8

```{r}
y=c(3,3,4,3,4,5,5,4)
logbin = function(x,param){log(dbinom(x,prob=param,size=20))}
MATH4753ouTrev0002::mymaxlik(lfun=logbin, x=y, param = seq(0,1,length = 1000), main = "binomial, n=20")
```


