---
title: "Lab2"
author: "Luis Mario Trevisi"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1

```{r}
getwd()
```

## Task 2

```{r}
EPAGAS <- read.csv("EPAGAS.csv")
head(EPAGAS)
```
## Task 3

making vector, and verfying results 

```{r}
mpg = EPAGAS$ï..MPG
z = (mpg-mean(mpg))/sd(mpg)
head(z)
round(mean(z), digits = 4)
var(z)
sd(z)
```

Possible Outliers:

```{r}
mpg = EPAGAS$ï..MPG
z = (mpg-mean(mpg))/sd(mpg)
mpg[abs(z)>=2 & abs(z)<=3]
```

 Definite Outliers

```{r}
mpg = EPAGAS$ï..MPG
z = (mpg-mean(mpg))/sd(mpg)
mpg[abs(z)>3]
```

 Plot

```{r}
library(lattice)
mpg = EPAGAS$ï..MPG
z = (mpg-mean(mpg))/sd(mpg)
mycol = ifelse(abs(z)>3, "Red",
        ifelse(abs(z)>=2 &abs(z)<=3,"Blue", "Black"))  
dotplot(mpg, col =mycol)
```

## Task 4

a) Box Plot 

```{r}
mpg = EPAGAS$ï..MPG
boxplot(mpg,notch = TRUE, horizontal = TRUE, col = 'black', main='Boxplot')
```


b) the proportion of data within 2 standard deviations of the mean of the mpg data.
$$Proportion \geq (1-\frac{1}{k^2}) = (1-\frac{1}{4}) = \frac{1}{4} $$
```{r}
k = 2
cheb = 1-(1/k^2)
cheb
```

 
c) Exact Number
```{r}
mpg = EPAGAS$ï..MPG
z = (mpg-mean(mpg))/sd(mpg)
percen = length(mpg[abs(z)<=2])/length(mpg)
percen
```
Thus Chebyshev agrees with the data

d) what proportion (according to the rule) of the data should be within 2 standard deviations of the mean?

it should be aprroximately 95%

e) How well does it correspond?
  
It corresponds really well as it is really close to the estimation value

f) Is the Empirical rule valid in this case? Why?

```{r}
mpg = EPAGAS$ï..MPG
histogram(mpg, main = 'Histogram')
```

for the empirical equation to be valid it have to pass two assumptions: it has to be symetric and be unimodal. in the case of this data, It is not symetric distribution and thus it is not valid.

