---
title: "R package"
author: "Luis Mario Trevisi"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction



Congratulations for getting this far. To complete the evidence that you have made a working R package please answer the following by using the supplied rmd  and upload the knitted html to CANVAS.

I will assume your package is called **MYPAC** and you have packaged and documented functions `myf1`, `myf2`, `myf3` and `myf4`.

Your actual package name and functions will obviously be called something else.

# First function

Please place your first function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r first}
MATH4753ouTrev0002::myhyper(100,10,5,8)

```


# Second function

Please place your second function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r second}
MATH4753ouTrev0002::myci(x=rnorm(7,mean=3,sd=1),conf.int=0.95)

```


# Third function

Please place your third function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r third}
MATH4753ouTrev0002::mychisim(n1 = 10, sigma1 = 3, mean1 = 5,iter = 1000,ymax = 0.1, x = 20, y = 0.1)

```


# Forth function

Please place your forth function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r forth}
MATH4753ouTrev0002::mychisim2(n1 = 10, n2 = 14, sigma1 = 3, sigma2 = 3, mean1 = 5,mean2 = 10, iter = 1000,ymax = 0.07,x = 40, y = 0.04,)

```

# The github repository



This is the address of my GITHUB repository:
<https://github.com/lmtrevisi/MATH4753ouTrev0002>

Replace this with your own address.
