---
title: "Lab6"
author: "Luis Mario Trevisi"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1

## Getting Working Directory
```{r}
getwd()
```

# Task 2

## Plot 4 normal curves
```{r}
layout(matrix(1:4, nr=2,nc=2))

layout.show(0)

curve(dnorm(x, mean=10,sd=4),xlim=c(-10,30))

curve(dnorm(x, mean=10,sd=2),xlim=c(-10,30))

curve(dnorm(x, mean=5,sd=10),xlim=c(-30,40))

curve(dnorm(x, mean=5,sd=0.5),xlim=c(0,10))
```
## Plot regions and probabilities

```{r}
layout(matrix(1:4, nr=2,nc=2))
# Region One
curve(dnorm(x, mean=0,sd=1),xlim=c(-5,5))
# x values corresponding to the x - cords of points on the curve
xcurve=seq(2,30,length=1000)

# Y values corresponding t0 the x values
ycurve=dnorm(xcurve,mean=0,sd=1)

# Fill in the polygon with the given vertices
polygon(c(2,xcurve,30),c(0,ycurve,0),col="Red")
# Area
prob=pnorm(30,mean=0,sd=1)-pnorm(2,mean=0,sd=1)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))

#Region Two
curve(dnorm(x, mean=4,sd=2),xlim=c(-10,15))
# x values corresponding to the x - cords of points on the curve
xcurve=seq(1,5,length=1000)

# Y values corresponding t0 the x values
ycurve=dnorm(xcurve,mean=4,sd=2)

# Fill in the polygon with the given vertices
polygon(c(1,xcurve,5),c(0,ycurve,0),col="Red")
# Area
prob=pnorm(5,mean=4,sd=2)-pnorm(1,mean=4,sd=2)
prob=round(prob,4)

# Click to paste the text onto the graph
text(-2.5,0.08, paste("Area = ", prob, sep=""))

#Region Three
curve(dnorm(x, mean=10,sd=4),xlim=c(-10,30))
# x values corresponding to the x - cords of points on the curve
xcurve=seq(-100,10,length=1000)

# Y values corresponding t0 the x values
ycurve=dnorm(xcurve,mean=10,sd=4)

# Fill in the polygon with the given vertices
polygon(c(-30,xcurve,10),c(0,ycurve,0),col="Red")
# Area
prob=pnorm(10,mean=10,sd=4)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))

#Region Four
curve(dnorm(x, mean=-2,sd=0.5),xlim=c(-5,2))
# x values corresponding to the x - cords of points on the curve
xcurve=seq(-3,-2,length=1000)

# Y values corresponding t0 the x values
ycurve=dnorm(xcurve,mean=-2,sd=0.5)

# Fill in the polygon with the given vertices
polygon(c(-3,xcurve,-2),c(0,ycurve,0),col="Red")
# Area
prob=pnorm(-2,mean=-2,sd=0.5)-pnorm(-3,mean=-2,sd=0.5)
prob=round(prob,4)

# Click to paste the text onto the graph
text(-3.5,0.5, paste("Area = ", prob, sep=""))
```

# Task 3
## On the one plotting surface overlay the following three plots
```{r}
curve(dgamma(x,shape=1,scale=1),xlim=c(0,10),ylim=c(0,1),col="Red",lwd=2,
ylab="Gamma density", main="Beta=1")
text(1,1,paste("alpha=",1),col="red")
curve(dgamma(x,shape=3,scale=1),xlim=c(0,10),ylim=c(0,1),add=TRUE,lwd=2)
text(1,0.9,paste("alpha=",3))
curve(dgamma(x,shape=5,scale=1),xlim=c(0,10),ylim=c(0,1),add=TRUE, col="Blue",lwd=2)
text(1,0.8,paste("alpha=",5),col="blue")
```

## Plot the following regions and probabilities in R
```{r}
# Make the plots
curve(dgamma(x,shape=3,scale=2),xlim=c(0,10),ylim=c(0,0.2),col="Red",lwd=2,
ylab="Gamma density", main="Beta=1")
text(1,0.9,paste("alpha=",1),col="red")

# x values corresponding to the x - cords of points on the curve
xcurve=seq(2,5,length=1000)

# Y values corresponding t0 the x values
ycurve=dgamma(xcurve,shape=3,scale=2)

# Fill in the polygon with the given vertices
polygon(c(2,xcurve,5),c(0,ycurve,0),col="Red")
# Area
prob=pgamma(5,shape=3,scale=2)-pgamma(2,shape=3,scale=2)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))


# Make the plots
curve(dgamma(x,shape=6,scale=3),xlim=c(0,10),ylim=c(0,0.1),col="Red",lwd=2,
ylab="Gamma density", main="Beta=1")
text(1,0.9,paste("alpha=",1),col="red")

# x values corresponding to the x - cords of points on the curve
xcurve=seq(1,4,length=1000)

# Y values corresponding t0 the x values
ycurve=dgamma(xcurve,shape=6,scale=3)

# Fill in the polygon with the given vertices
polygon(c(1,xcurve,4),c(0,ycurve,0),col="Red")
# Area
prob=pgamma(4,shape=6,scale=3)-pgamma(1,shape=6,scale=3)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))


# Make the plots
curve(dgamma(x,shape=2,scale=4),xlim=c(0,20),ylim=c(0,0.1),col="Red",lwd=2,
ylab="Gamma density", main="Beta=1")
text(1,0.9,paste("alpha=",1),col="red")

# x values corresponding to the x - cords of points on the curve
xcurve=seq(3,6,length=1000)

# Y values corresponding t0 the x values
ycurve=dgamma(xcurve,shape=2,scale=4)

# Fill in the polygon with the given vertices
polygon(c(3,xcurve,6),c(0,ycurve,0),col="Red")
# Area
prob=pgamma(6,shape=2,scale=4)-pgamma(3,shape=2,scale=4)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))


```

# Task 4

## Plots
```{r}
layout(matrix(1:4, nr=2,nc=2))
curve(dchisq(x,df=1),xlim=c(0,10),ylim=c(0,1),col="Red",lwd=2,
ylab="Chisq density", main="df=1")
text(1,1,paste("df=",2))

curve(dchisq(x,df=2),xlim=c(0,10),ylim=c(0,1),col="Red",lwd=2,
ylab="Chisq density", main="df=2")
text(1,1,paste("df=",2))

curve(dchisq(x,df=4),xlim=c(0,10),ylim=c(0,0.2),col="Red",lwd=2,
ylab="Chisq density", main="df=4")
text(1,1,paste("df=",2))

curve(dchisq(x,df=20),xlim=c(10,40),ylim=c(0,0.1),col="Red",lwd=2,
ylab="Chisq density", main="df=20")
text(1,1,paste("df=",2))
```

## Plot regions and probabilities in R 

```{r}
# Make Plot
curve(dchisq(x,df=2),xlim=c(0,10),ylim=c(0,1),col="Red",lwd=2,
ylab="Chisq density", main="df=2")
text(1,1,paste("df=",2))
# x values corresponding to the x - cords of points on the curve
xcurve=seq(2,4,length=1000)

# Y values corresponding t0 the x values
ycurve=dchisq(xcurve,df = 2)

# Fill in the polygon with the given vertices
polygon(c(2,xcurve,4),c(0,ycurve,0),col="Red")
# Area
prob=pchisq(4,df = 2)-pchisq(2,df=2)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))

# Make Plot
curve(dchisq(x,df=3),xlim=c(0,10),ylim=c(0,0.4),col="Red",lwd=2,
ylab="Chisq density", main="df=2")
text(1,1,paste("df=",3))
# x values corresponding to the x - cords of points on the curve
xcurve=seq(3,5,length=1000)

# Y values corresponding t0 the x values
ycurve=dchisq(xcurve,df = 3)

# Fill in the polygon with the given vertices
polygon(c(3,xcurve,5),c(0,ycurve,0),col="Red")
# Area
prob=pchisq(5,df = 3)-pchisq(3,df=3)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))


# Make Plot
curve(dchisq(x,df=20),xlim=c(0,40),ylim=c(0,.1),col="Red",lwd=2,
ylab="Chisq density", main="df=2")
text(1,1,paste("df=",20))
# x values corresponding to the x - cords of points on the curve
xcurve=seq(10,21,length=1000)

# Y values corresponding t0 the x values
ycurve=dchisq(xcurve,df = 20)

# Fill in the polygon with the given vertices
polygon(c(10,xcurve,21),c(0,ycurve,0),col="Red")
# Area
prob=pchisq(21,df = 20)-pchisq(10,df=20)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))
```

# Task 5

```{r}
layout(matrix(1:4, nr=2,nc=2))
curve(dweibull(x,shape=1,scale=1),xlim=c(0,10),ylim=c(0,3),col="Red",lwd=2,)
text(1,1,paste("alpha=",1),col="red")
curve(dweibull(x,shape=3,scale=1),xlim=c(0,10),ylim=c(0,3),lwd=2)
text(1,0.9,paste("alpha=",3))
curve(dweibull(x,shape=5,scale=1),xlim=c(0,10),ylim=c(0,3), col="Blue",lwd=2)
text(1,0.8,paste("alpha=",5),col="blue")
curve(dweibull(x,shape=7,scale=1),xlim=c(0,10),ylim=c(0,3), col="orange",lwd=2)
text(1,0.8,paste("alpha=",7),col="orange")
```

## Calculate any three areas and probabilities 
```{r}
# Make the plots
curve(dweibull(x,shape=3,scale=2),xlim=c(0,10),ylim=c(0,0.8),col="Red",lwd=2)
text(1,0.9,paste("alpha=",1),col="red")

# x values corresponding to the x - cords of points on the curve
xcurve=seq(2,5,length=1000)

# Y values corresponding t0 the x values
ycurve=dweibull(xcurve,shape=3,scale=2)

# Fill in the polygon with the given vertices
polygon(c(2,xcurve,5),c(0,ycurve,0),col="Red")
# Area
prob=pweibull(5,shape=3,scale=2)-pweibull(2,shape=3,scale=2)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))


# Make the plots
curve(dweibull(x,shape=6,scale=3),xlim=c(0,10),ylim=c(0,1),col="Red",lwd=2)
text(1,0.9,paste("alpha=",1),col="red")

# x values corresponding to the x - cords of points on the curve
xcurve=seq(1,4,length=1000)

# Y values corresponding t0 the x values
ycurve=dweibull(xcurve,shape=6,scale=3)

# Fill in the polygon with the given vertices
polygon(c(1,xcurve,4),c(0,ycurve,0),col="Red")
# Area
prob=pweibull(4,shape=6,scale=3)-pweibull(1,shape=6,scale=3)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))


# Make the plots
curve(dweibull(x,shape=2,scale=4),xlim=c(0,20),ylim=c(0,0.3),col="Red",lwd=2)
text(1,0.9,paste("alpha=",1),col="red")

# x values corresponding to the x - cords of points on the curve
xcurve=seq(3,6,length=1000)

# Y values corresponding t0 the x values
ycurve=dweibull(xcurve,shape=2,scale=4)

# Fill in the polygon with the given vertices
polygon(c(3,xcurve,6),c(0,ycurve,0),col="Red")
# Area
prob=pweibull(6,shape=2,scale=4)-pweibull(3,shape=2,scale=4)
prob=round(prob,4)

# Click to paste the text onto the graph
text(3,0.08, paste("Area = ", prob, sep=""))


```

# Task 6

## Plot Four Shapes

```{r}
layout(matrix(1:4, nr=2,nc=2))
curve(dbeta(x,shape=4,shape2=1),xlim=c(0,10),ylim=c(0,5),col="Red",lwd=2,
)

curve(dbeta(x,shape=3,shape2=1),xlim=c(0,10),ylim=c(0,5),lwd=2)

curve(dbeta(x,shape=5,shape2=1),xlim=c(0,10),ylim=c(0,5), col="Blue",lwd=2)
curve(dbeta(x,shape=7,shape2=3),xlim=c(0,10),ylim=c(0,5), col="orange",lwd=2)
```

## Plot the following regions and probabilities in R
```{r}
# Make the plots
curve(dbeta(x,shape1=3,shape2=2),xlim=c(0,2),ylim=c(0,3),col="Red",lwd=2)


# x values corresponding to the x - cords of points on the curve
xcurve=seq(0.3,0.6,length=1000)

# Y values corresponding t0 the x values
ycurve=dbeta(xcurve,shape1=3,shape2=2)

# Fill in the polygon with the given vertices
polygon(c(0.3,xcurve,0.6),c(0,ycurve,0),col="Red")
# Area
prob=pbeta(0.6,shape1=3,shape2=2)-pbeta(0.3,shape1=3,shape2=2)
prob=round(prob,4)

# Click to paste the text onto the graph
text(0.3,1.5, paste("Area = ", prob, sep=""))


# Make the plots
curve(dbeta(x,shape1=6,shape2=3),xlim=c(0,2),ylim=c(0,3),col="Red",lwd=2)


# x values corresponding to the x - cords of points on the curve
xcurve=seq(0.5,0.7,length=1000)

# Y values corresponding t0 the x values
ycurve=dbeta(xcurve,shape1=6,shape2=3)

# Fill in the polygon with the given vertices
polygon(c(0.5,xcurve,0.7),c(0,ycurve,0),col="Red")
# Area
prob=pbeta(0.7,shape1=6,shape2=3)-pbeta(0.5,shape1=6,shape2=3)
prob=round(prob,4)

# Click to paste the text onto the graph
text(0.25,1.5, paste("Area = ", prob, sep=""))


# Make the plots
curve(dbeta(x,shape1=2,shape2=4),xlim=c(0,2),ylim=c(0,3),col="Red",lwd=2)


# x values corresponding to the x - cords of points on the curve
xcurve=seq(0.3,0.6,length=1000)

# Y values corresponding t0 the x values
ycurve=dbeta(xcurve,shape1=2,shape2=4)

# Fill in the polygon with the given vertices
polygon(c(0.3,xcurve,0.6),c(0,ycurve,0),col="Red")
# Area
prob=pbeta(0.6,shape1=2,shape2=4)-pbeta(0.3,shape1=2,shape2=4)
prob=round(prob,4)

# Click to paste the text onto the graph
text(0.3,1.5, paste("Area = ", prob, sep=""))


```

# Task 7
```{r}
MATH4753ouTrev0002::myncurve(mu=10,sigma=5, a=6)
```

